{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex
Some language changes + appl_fpcr_bspline_nharm2

	All functions $f$ satisfying the above condition are called square-integrable functions. Moreover, it ensures that a random function has a finite second moment so that the variance and the covariance function can be defined. Its inner product is defined as

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis without loss of generality. We also focus on the interval [0,1] for the purpose of this paper.	A random function defined on $\mathbb{L}^2[0,1]$ can be represented as
	a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ which is defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample sapce with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$. The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations. For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.

@@

	\subsection{Bases of $\mathbb{L}^2$ {\color{orange}Basis Representation for Functions}} 
	{\color{red} Maybe change title due to monomial and bspline basis not fulfilling this property.}
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Two examples of bases that are often used in practice to express / approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^k \quad i \in \mathcal{I}
	\end{equation}
	The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
	The shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
	 There exists problems of collinearity of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. Therefore, regarding the use, this may be useful for relatively simple functions. However, the small number of degrees makes it impossible to capture pronounced local peculiarities {\color{orange} (Isn't it good as thinking of the Taylor? The use of MB for local expansion? Need to check.)} and leads to undesirable behaviour at the tails such as Taylor expansion. (cf. \cite{ramsay_functional_2005})

	\paragraph{Fourier Basis}
	Fourier series basically decomposes a periodic function with a weighted summation of trigonometric funtions. Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between 0 and 1, and we can then apply the Fourier series to approximate the function for smoothing. As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions. That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}

	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.  {\color{blue} Motivate from fourier series}

@@

	Consider the case of a dataset which is containing observations of an underlying continuous process, measured at some discrete points $t_{j,i}$:

@@

	This measurement set can be viewed as set of discretized approximations of the underlying functional process:
 $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at the discrete measurement points. 
As in the finite dimensional setting, the concept of identically distributed and independent data is important. This concept generalizes intuitively to the case of functional data using the concepts for general random variables which is needed to conduct inference. {\color{red} Explain this better!}\\  The introduced concept of basis expansion of functions allow to express each observation $x_1$ as a realization of $X_1$, a random function of $\mathbb{L}^2[0,1]$.

	%In functional data analysis the concept of a data set can include not only realizations of scalar random variables, but also realizations of random functions. In the following, all random functions are assumed to realize in $\mathbb{L}^2$.

	An example of such a dataset could be the dataset of 60 NIR-spectra of gasoline samples. Together with a set of responses, this then can be used to perform FLR, as will be subject of the simulation and application.

	% COMMENT: Maybe mention both NIR and WienerProcess? 
	%An example of one such data set could be a set of $n$ independent realizations of a Wiener-process and $n$ associated scalar variables that could be subject of a regression analysis with respect to the corresponding realizations of the Wiener process. A definition and a plotted example for the Wiener process are given in \ref{Wiener}.

@@

\subsection{Wiener Process}\label{Wiener}
A Wiener process $W_t$ is a real-valued continuous-time stochastic process {\color{red} ... This is wikipedia, look for right citation!}
It is characterized by the following properties.

\begin{multicols}{2}
	\begin{enumerate}
		\item $W_0 = 0$
		\item $\forall t > 0 W_{t+u} - W_t \perp\!\!\!\perp W_s \forall s \leq t$
		\item $W_{t+u} - W_t \sim \mathcal{N}(0,u)$
		\item $W_t$ is continuous in $t$
	\end{enumerate}
\end{multicols}

\begin{figure}[H]\label{Wiener_plot}
	\includegraphics[width = \textwidth]{../Graphics/Wiener_plot.pdf}
	\caption{25 i.i.d. realizations of a Wiener Process on $[0,1]$}
\end{figure}

>>>>

	%All functions $f$ satisfying the above condition are called square-integrable functions. 
	This ensures that a random function has a finite second moment so that the variance and covariance functions can be defined. Its inner product is defined as

@@

	$\mathbb{L}^2[0,1]$ is the function space that is most often used for theoretical considerations in functional data analysis but analogous constructions can be made for every closed interval of $\mathbb{R}$. 
	%Therefore, we focus on the interval $[0,1]$ without loss of generality for the purpose of this paper. 
	A random function defined on $\mathbb{L}^2[0,1]$ is a function $X : \Omega \rightarrow \mathbb{L}^2[0,1]$ defined on a common probability space $(\Omega, \mathcal{A}, P)$ where $\Omega$ is a sample space with $\sigma$-algebra $\mathcal{A}$ and a probability space $P$. The realized $X(\omega)(t)$ for every $t \in [0,1]$ is called a sample curve for the process. The collection of such sample curves constitutes a functional data set.
	%Trivially, it is possible to extend this to other closed intervals on the reals line, but there are also more complex generalizations. For the purpose of this paper we will focus on the typical case and assume that random functions are random variables realizing in $\mathbb{L}^2$ for some closed interval of the real numbers.

@@

	\subsection{Representing a Function in terms of a Basis} 
	As previously described, a basis of a Hilbert space can be used to express elements of the space using the corresponding Fourier expansion. Three examples of bases that are often used in practice to approximate elements of $\mathbb{L}^2[0,1]$  are explained in the following.

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^k \quad i \in \mathcal{I}
	\end{equation}
	The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). {\color{blue} Taylor expansion as motivation}\\ 
	The shift parameter $\alpha$ is specified to be the center of the interval subject to approximation.
	 There exists problems of collinearity of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. Therefore, regarding the use, this may be useful for relatively simple functions. However, the small number of degrees makes it impossible to capture pronounced local peculiarities {\color{orange} (Isn't it good as thinking of the Taylor? The use of MB for local expansion? Need to check.)} and leads to undesirable behavior at the tails such as Taylor expansion. (cf. \cite{ramsay_functional_2005})

	\paragraph{Fourier Basis}
	Fourier series basically decomposes a periodic function with a weighted summation of trigonometric functions. Imagine that an arbitrary function in $\mathbb{L}^2[0,1]$ has one or more cycles between 0 and 1, and we can then apply the Fourier series to approximate the function for smoothing. As the series originated from the amplitude-phase form regarding cosine functions, it can be rewritten by sine and cosine form through a simple trigonometry formula, which restricts the use of an odd number of Fourier basis functions. That is why the Fourier basis for $\mathbb{L}^2[0,1]$ is given by the following sequence of functions defined on $[0,1]$.
	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}

	Therefore, its basis functions inherits a repeating behavior which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.  {\color{blue} Motivate from Fourier series}

@@

	Consider the case of a data set containing observations $X_i(t)$ of a random function $X(\omega)(t)$, measured at discrete points $t_{j,i}$:

@@

 	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. Therefore, this can be seen as set of discretized approximations of the realizations of a random function.
	As in the finite dimensional setting, the concept of identically distributed and independent data is important. This concept generalizes to the case of functional data using the concepts for general random variables.

	An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples. Together with a set of responses, this then can be used to perform functional linear regression, as will be subject of the simulation and application.

@@
